Make any stupid plot you want

### 2021-04-13 draft/sections/intro.tex
figure caption

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}
\begin{figure}[h]
    \includegraphics[width=1\textwidth]{figures/intro/functions.png}
    \caption{Visualizations are made up of transformations from data into visual representation. These functions are are both transformations of individual data values to visual representation, such as date to x position or latitude to y position, and the assembly of all these transformations into a visual mark, such as a line or point. The same variable can be mapped in different ways, for example line is mapped to a color in the scatter plot and to y position in the line plot.}
    \label{fig:intro_artist}
\end{figure}
Visualization is the transformation of data into visual representation. As illustrated by \autoref{fig:intro_artist}, these translations are both at the level of the individual variable and the entire record. In the case of the scatter plot, the latitude and longitude are encoded as the x and y position, respectively, while the temperature and station are represented by the face and edge colors. A row in the table is collectively encoded as a point mark. None of these encodings are fixed, as evidenced by temperature being translated into the y value in the case of the line plot. The station is now the source of the color of the entire line, and the date is the x position. As with scatter, the encodings of the individual transformations, which again are on values from the same record in the table, are composited into a line mark. It is these raw transformations from data space to visualization space that are implemented by building block level visualization libraries, named as such because the functions provided by the library can be composited in any number of ways to yield visualizations \cite{wongsuphasawatNavigatingWideWorld2021}. We propose that like physical building blocks, building block libraries must provide a collection of well defined pieces that can be composed in whichever ways the blocks fit together. We specify that a valid visualization block is a structure preserving transformation from data to visual space, and we define structure in terms of \textit{continuity} and \textit{equivariance}. We then use this model to develop a design specification for the components of a building block visualization library. The notion of self contained, inherently modular, building blocks lends itself naturally to a functional paradigm of visualization \cite{hughesWhyFunctionalProgramming1989}. We adopt a functional model for a redesign because the lack of side effects means functional architecture can be evaluated for correctness, functional programs tend to be shorter and clearer, and are well suited to distributed, concurrent, and on demand tasks\cite{huHowFunctionalProgramming2015}.

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}
\begin{figure}[h]
    \includegraphics[width=1\textwidth]{figures/intro/functions.png}
    \caption{Visualizations are made up of transformations from data into visual representation. These functions transform individual data values to visual representation, such as date to x position or latitude to y position. These functions are composed into the assembly of all these transformations into a visual mark, such as a line or point. %%% break this out into seperate sentences to break 
    The same variable can be mapped in different ways, for example line is mapped to a color in the scatter plot and to y position in the line plot.}
    \label{fig:intro_artist}
\end{figure}
Visualization is the transformation of data into visual representation. As illustrated by \autoref{fig:intro_artist}, these translations are both at the level of the individual variable and the entire record. In the case of the scatter plot, the latitude and longitude are encoded as the x and y position, respectively, while the temperature and station are represented by the face and edge colors. A row in the table is collectively encoded as a point mark. None of these encodings are fixed, as evidenced by temperature being translated into the y value in the case of the line plot. The station is now the source of the color of the entire line, and the date is the x position. As with scatter, the encodings of the individual transformations, which again are on values from the same record in the table, are composited into a line mark. It is these raw transformations from data space to visualization space that are implemented by building block level visualization libraries, named as such because the functions provided by the library can be composited in any number of ways to yield visualizations \cite{wongsuphasawatNavigatingWideWorld2021}. We propose that like physical building blocks, building block libraries must provide a collection of well defined pieces that can be composed in whichever ways the blocks fit together. We specify that a valid visualization block is a structure preserving transformation from data to visual space, and we define structure in terms of \textit{continuity} and \textit{equivariance}. We then use this model to develop a design specification for the components of a building block visualization library. The notion of self contained, inherently modular, building blocks lends itself naturally to a functional paradigm of visualization \cite{hughesWhyFunctionalProgramming1989}. We adopt a functional model for a redesign because the lack of side effects means functional architecture can be evaluated for correctness, functional programs tend to be shorter and clearer, and are well suited to distributed, concurrent, and on demand tasks\cite{huHowFunctionalProgramming2015}.
